 Total Team Spending and Profitability Results in a Higher League Ranking in the English Premier League

### 2024-04-19 paper/paper.qmd
Committing all cahnges up to date. 04-19-2024 @2:26am.

@tbl-7 shows the table of the coefficients after running the linear model summary.
```{r}
#| echo: false
#| warning: false
#| results: 'hide'

@@

kable(coefs, format = "latex", booktabs = TRUE) |>
  kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10)

@@

>>>>

@tbl-7 shows the table of the coefficients after running the linear model summary.
```{r}
#| echo: false
#| warning: false
#| include: false

@@

kable(coefs, booktabs = TRUE, align = c("l", rep("r", 6)), "latex", longtable = TRUE) |>
  kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10)

@@

```{r}
#| label: tbl-8
#| tbl-cap: Actual vs Predicted Points for English Premier League Teams Based on Home Attendance, Wage Bill, and Market Value, Sorted by Current League Ranking in Descending Order
#| echo: false
#| warning: false

# Predict points using the model
analysis_data$predicted_pts <- predict(model, newdata = analysis_data)

# Display actual vs predicted points sorted by actual points descending
result_table <- analysis_data |> 
  select(team, pts, predicted_pts) |>
  arrange(desc(pts))

# Format table with LaTeX and apply additional styling
kable(result_table, booktabs = TRUE, align = c("l", rep("r", 6)), "latex", longtable = TRUE) |>
  kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10)
```
